\newpage	
\addcontentsline{toc}{section}{Referencias}		% sino no figura en el TOC

\begin{thebibliography}{100}

	\bibitem{wang}
 	 	Kai Wang, Boris Babenko and Serge Belongie,
	 	\emph{``End-to-End Scene Text Recognition''},
		IEEE International Conference on Computer Vision (ICCV), 
		Barcelona, España,
		2011.
		
	\bibitem{WB10}
 	 	Kai Wang and Serge Belongie,
	 	\emph{``Word spotting in the wild''},
		In ECCV, 2010.
		
	\bibitem{fischler}
 	 	M.A. Fischler and R.A. Elschlager,
	 	\emph{``The representation and matching of pictorial
structures''},
		IEEE Transactions on Computer, 
		22(1):67–92,
		Enero 1973.
		
	\bibitem{Bis07}
		Christopher M. Bishop.
		\emph{``Pattern Recognition and Machine Learning (Information Science and Statistics)''}.
		Springer, Octubre 2007.
		
	\bibitem{dCBV09}
		T. E. de Campos, B. R. Babu, and M. Varma.
		Character recognition in natural images.
		In \emph{``Proceedings of the International Conference on Computer Vision Theory and Applications, Lisbon, Portugal,''}
		February, 2009.
		
	\bibitem{KGK^{+}07}
		Sunil Kumar, Rajat Gupta, Nitin Khanna, Santanu Chaudhury, and Shiv Dutt Joshi.
		\emph{``Text extraction and document image segmentation using matched wavelets and mrf model.''}
		\textit{IEEE Transactions on Image Processing}, 16(8):2117-2128, 2007.
	
	\bibitem{DT05}
		Navneet Dalal \& Bill Triggs.
		\emph{``Histograms of oriented gradients for human detection.''}
		In Cordelia Schmid, Stefano Soatto, and Carlo Tomasi, editors, \textit{International Conference on Computer Vision \& Pattern Recognition}, volume 2, pages 886-893, INRIA Rh\^{o}ne-Alpes, ZIRST-655, av. de l'Europe, Montbonnot-38334, June 2005.
		
	\bibitem{PSH2011}
		J. Pradeep, E. Shrinivasan \& S. Himavathi,
		\emph{``Diagonal Based Feature Extraction for Handwritten Alphabets Recognition System Using Neural Network''},
		International Journal of Computer Science \& Information Technology(IJCSIT),
		vol.3, No 1, February 2011.
		
	\bibitem{Suen86}
		C. Y. Suen,
		\emph{``Character recognition by computer and applications''},
		in Handbook of Patter Recognition and Image Processing,
		New York: Academic,
		pp. 569-586,
		1986

	
	%\bibitem{RVJA2012}
	%	R. Verma \& J. Ali,
	%	\emph{``A-Survey of Feature Extraction and Classification Techniques in OCR Systems''},
	%	International Journal of Computer Applications \& Information Technology,
	%	Vol. I, Issue III,
	%	November 2012 (ISSN: 2278-7720).
		
	\bibitem{Heutte98}
		L. Heutte, T. Paquet, J. V. Moreau, Y. Lecourtier and C. Olivier,
		\emph{``Structural/statistical feature based vector for handwritten character recognition''},
		Pattern Recognition Letters,
		Vol. 19(7), pp. 629-641,
		1998.
		
	\bibitem{Hussain72}
		A. B. S. Hussain, G. T. Toussaint and R. W. Donaldson,
		\emph{``Results obtained using a simple character recognition procedure on Munson’s handprinted data''},
		IEEE Transactions on Computers, pp. 201-205,
		1972.
		
	\bibitem{Glauberman56}
		M. H. Glauberman,
		\emph{``Character recognition for business
machines''},
		Electronics,
		Vol. 29, pp. 132-136,
		1956.
		
	\bibitem{TR93}
		R. Tarling and R. Rohwer,
		\emph{``Efficient use of training data in
the n-tuple recognition method''},
		Electronics Letters,
		Vol. 29(24), pp. 2093-2094,
		1993
		
	\bibitem{RP94}
		J. Rocha and T. Pavlidis,
		\emph{``A shape analysis model with applications to a character recognition system''},
		IEEE Transactions on PAMI,
		Vol. 16(4), pp. 393-404, 
		1994.
		
	\bibitem{Amin2000}
		A. Amin,
		\emph{``Recognition of printed Arabic text based on global features and decision tree learning techniques''},
		\textit{Patter Recognition},
		Vol. 33, pp. 1309-1323,
		2000.
	
	\bibitem{NNSJ}
		Nadira Muda, Nik Kamariah, Nik Ismail, Siti Azami Abu Bakar, Jasni Mohamad Zain,
		\emph{``Optical Character Recognition By Using Template Matching(Alphabet)''},
		Universiti Malaysia Pahang.
		
	\bibitem{SA96}
		S. Lucas, A. Amiri
		\emph{``Statistical Syntactic Methods for High Performance OCR''}
		Vision, Image and Signal Processing, IEE Proccedings,
		vol. 134, Issue 1, pp. 23-30,
		February 1996.
		
	\bibitem{RYVY2010}
		Raghuraj Singh, C. S. Yadav, Prabhat Verma, Vibhash Yadav,
		\emph{``Optical Character Recognition (OCR) for Printed Devnagari Script Using Artificial Neural Network''},
		International Journal of Computer Science \& Communication,
		January-June  2010.
	
	\bibitem{Eikvil}
		Line Eikvil.
		\emph{``Optical Character Recognition''}.
		\url{http://www.nr.no/~eikvil/OCR.pdf}.
		December, 1993.
		
	\bibitem{GKurt}
		Dr. Gordon Kurtenbach (2010).
		\emph{``Pen-Based Computing''}.
		\emph{XRDS}, vol.16, num.4, pp.14-20.
		Obtenido de \url{http://www.autodeskresearch.com/pdf/penbasedcomputing-kurtenbach.pdf}.
		
	\bibitem{x-root}
		Andor Grei{\ss}l.(2009).
		\emph{Cardreader}(v2.0.10)[Mobile Application Software].
		Obtenido de \url{https://itunes.apple.com/de/app/id333992036?mt=8}
		
	\bibitem{arh-anpr}
		ARH Inc.
		\emph{The CARMEN\textregistered Parking ANPR Software}[Computer Software].
		Obtenido de \url{http://www.anpr.net/anpr_09/anpr_parking.html}
		
	\bibitem{arh-passport}
		ARH Inc.
		\emph{PRM(Passport Reader Multireader)}[Computer Device].
		Obtenido de \url{http://www.passport-reader.com/prm_passport_reader.html}
		
	\bibitem{arh-card}
		ARH Inc.
		\emph{Card Reader}[Computer Device].
		Obtenido de \url{http://www.passport-reader.com/card_reader.html}
	
	\bibitem{creaceed}
		Creaceed S.P.R.L (2010).
		\emph{Prizmo}(v3.1.5)[Mobile Application Software].
		Obtenido de \url{https://itunes.apple.com/gb/app/prizmo-scanning-ocr-speech/id366791896?mt=8}
		
	\bibitem{sunnyside}
		SUNNYSIDESOFT (2013).
		\emph{VirtualTablet Lite (S-Pen)}(v1.2)[Mobile Application Software].
		Obtenido de \url{https://play.google.com/store/apps/details?id=com.sunnysidesoft.VirtualTablet}
		
	\bibitem{gbook}
		Google Inc.(2004).
		\emph{Google Books}[Web Service].
		Obtenido de \url{http://books.google.com/}.
		
	\bibitem{Tauschek}
		G. Tauschek,
		\emph{``Reading Machine''},
		U.S. Patent 2026329,
		December 1935.
		
	\bibitem{Handel}
		P. W. Handel,
		\emph{``Statistical machine''}
		U.S. Patent 1915993,
		June 1933.
	
	\bibitem{Tesseract}
		Google Inc.(2005).
		\emph{``Tesseract''}
		Obtenido de \url{https://code.google.com/p/tesseract-ocr/}
		
	\bibitem{YoutubeStats}
	Google Inc.
	\emph{``Youtube statistics''}.
	Obtenido de \url{http://www.youtube.com/yt/press/es/statistics.html}
	
	\bibitem{Websites}
	Google Inc. 
	Official Blog.
	Obtenido de \url{http://googleblog.blogspot.com.ar/2008/07/we-knew-web-was-big.html}
	
	\bibitem{GoogleSearches}
	Statistic Brain.
	\emph{``Google Annual Search Statistics''}(2014).
	Obtenido de \url{http://www.statisticbrain.com/google-searches/}
	
	\bibitem{DP97}
		Domingos, P. y M. Pazzani (1997).
		\emph{``On the optimality of the simple bayesian classifier under zero-one loss''}. \textit{Machine Learning} 29, pp. 103-130.
		
	\bibitem{SpamPaper}
		T. S. Guzella, W. M. Caminhas.
		\emph{A review of machine learning approaches to Spam filtering}.
		Expert Systems with Applications.
		2009.
		
	\bibitem{BrownLowe07}
		Brown, M. and Lowe, D. (2007).
		\emph{``Automatic panoramic image stitching using invariant features''}.
		\textit{International Journal of Computer Vision},
		74(1):59–73.
	
	\bibitem{FPZ07}
		Fergus, R., Perona, P., and Zisserman, A. (2007).
		\emph{``Weakly supervised scale-invariant learning of models for visual recognition''}.
		\textit{International Journal of Computer Vision},
		71(3):273–303.
		
	\bibitem{Breiman01}
		Breiman, L.
		\emph{``Random Forests''}.
		Machine Learning 45(1), 5-32.
		January 2001.
		
				
	\bibitem{HOGImages}
		Levi G., (2013, August 18).
		\emph{``A Short introduction to descriptors''}[blog post].
		Obtenido de \url{http://gilscvblog.wordpress.com/2013/08/18/a-short-introduction-to-descriptors/}.
	
	\bibitem{Ozuysal}
		Ozuysal, M., Calonder, M., Lepetit, V. \& Fua, P.
		\emph{``Fast Keypoint Recognition using Random Ferns''}.
		IEEE Transactions on Pattern Analysis and Machine Intelligence,
		32, 448-461 (2010)
		
	\bibitem{DAB}
		Donoser, M., Arth, C. \& Bischof, H.
		\emph{``Detecting, Tracking and Recognizing License Plates''}.
		Institute for Computer Graphic and Vision.
		
	\bibitem{Nadejda}
		Nadejda S. Roubtsova , Rob G.J. Wijnhoven and Peter H.N. de With.
		\emph{``Integrated Text Detection and Recognition in Natural Images''}.
		
	\bibitem{LoweDavid04}
		Lowe, David G. (2004).
		\emph{``Distinctive Image Features from Scale-Invariant Keypoints''}.
		\textit{International Journal of Computer Vision.}
		
	\bibitem{LoweDavid99}
		Lowe, David G. (1999).
		\emph{``Object recognition from local scale-invariant features''}.
		Proceedings of the International Conference on Computer Vision 2.
		pp. 1150–1157.
		
	\bibitem{SJC08}
		J. Shotton, M. Johnson, and R. Cipolla.
		\emph{``Semantic texton forests for image categorization and segmentation''}.
		In \textit{CVPR}, 2008.
		
	\bibitem{OFL07}
		M. Ozuysal, P. Fua, and V. Lepetit.
		\emph{``Fast keypoint recognition in ten lines of code''}.
		In \textit{CVPR}, 2007.
		
	\bibitem{QuinlanID3}
		J. R. Quinlan.
		\emph{Induction of Decision Trees}.
		Machine Learning 1: 81-106.
		March 1986.
		
	\bibitem{QuinlanC45}
		J. R. Quinlan.
		\emph{C4.5: Programs for Machine Learning}.
		Morgan Kaufmann Publishers, 1993.
		
	\bibitem{PDomingo}
		P. Domingo.
		\emph{``A Few Useful Things to Know about Machine Learning''}.
		Department of Computer Science and Engineering.
		University of Washington.
		
	\bibitem{GPP03}
		B. Gatos, I. Pratikakis and S. Perantonis.
		\emph{``Towards Text Recognition in Natural Scene Images''}.
		Computational Intelligence Laboratory, Institute of Informatics and Telecommunications.
		
	\bibitem{LNJM}
		L. Neumann and J. Matas.
		\emph{``Real-Time Scene Text Localization and Recognition''}.
		In \textit{CVPR}, 2012.
		
	\bibitem{PiotrD}
		Piotr Dollár.
		\emph{Piotr's Image and Video Matlab Toolbox (PMT)}.
		Obtenido de \url{http://vision.ucsd.edu/~pdollar/toolbox/doc/index.html}. 
		
	\bibitem{LBreiman96}
		L. Breiman.
		\emph{Bagging Predictors}.
		Septiembre 1994.
		
		
		
				
\end{thebibliography}